Checkpoint 4

### 2020-05-01 Draft-Report.Rmd
Update Draft-Report.Rmd

Our data set includes not only repeated measures on our response variable $Y$ for each state, it also includes corresponding observations for our preditor variables as well. In order to increase the complexity of our model to include these aspects we will use the model strcuture below as a fundamental start point:

$$
\begin{split}
Y_{ij} | b_0, b_1, \beta_0, \beta_1, \sigma_w, \sigma_{0b}, \sigma_{1b} & \sim N(b_{0i} + b_{1i} X_{ij}, \; \sigma_w^2) \\
b_{0i} | \beta_0, \sigma_{0b} & \stackrel{ind}{\sim} N(\beta_0, \sigma_{0b}^2) \\
b_{1i} | \beta_1, \sigma_{1b} & \stackrel{ind}{\sim} N(\beta_1, \sigma_{1b}^2) \\
\beta_0 & \sim N(..., ...) \\
\beta_1 & \sim N(..., ...) \\
\sigma_w & \sim Exp(...) \\
\sigma_{0b} & \sim Exp(...) \\
\sigma_{1b} & \sim Exp(...) \\
\end{split}
$$
With this structure our model will be able to account for the differing intercepts based on the day and also the differing slopes we expect to see by state.

@@

prediction_summary(y = Finaldata$ChinaVirusInterest,
  yrep = pred_complex)
```
Finallly in our analysis of the model we see that the MAE of this model is 9.01. Our within-50 rate is 0.60 which means that 60%  of the predictions that fall within our middle 50% of our predictive model. Our within our 95 rate is .97 which means that 97% of our predictions fall within the middle 95% of our predictive model.

@@

actual_FL_pred
```
To test the accuracy of the complex model we decided to test our prediction on one case too. We chose Florida as our test state and as you can see from the summaries above our predictions are
relatively close. The actual mean of interest in the term China Virus in Florida is 47.625 and our model predicted 46.10, this is only a 1.5 difference!

>>>>

**Comment:** Our data set includes not only repeated measures on our response variable $Y$ for each state, it also includes corresponding observations for our preditor variables as well. In order to increase the complexity of our model to include these aspects we will use the model strcuture below as a fundamental start point:

$$
\begin{split}
Y_{ij} | b_0, b_1, \beta_0, \beta_1, \sigma_w, \sigma_{0b}, \sigma_{1b} & \sim N(b_{0i} + b_{1i} X_{ij}, \; \sigma_w^2) \\
b_{0i} | \beta_0, \sigma_{0b} & \stackrel{ind}{\sim} N(\beta_0, \sigma_{0b}^2) \\
b_{1i} | \beta_1, \sigma_{1b} & \stackrel{ind}{\sim} N(\beta_1, \sigma_{1b}^2) \\
\beta_0 & \sim N(..., ...) \\
\beta_1 & \sim N(..., ...) \\
\sigma_w & \sim Exp(...) \\
\sigma_{0b} & \sim Exp(...) \\
\sigma_{1b} & \sim Exp(...) \\
\end{split}
$$

**Comment:** With this structure our model will be able to account for the differing intercepts based on the day and also the differing slopes we expect to see by state.

@@

prediction_summary(y = Finaldata$ChinaVirusInterest,
  yrep = pred_complex)
```
**Comment:** Finallly in our analysis of the model we see that the MAE of this model is 9.01. Our within-50 rate is 0.60 which means that 60%  of the predictions that fall within our middle 50% of our predictive model. Our within our 95 rate is .97 which means that 97% of our predictions fall within the middle 95% of our predictive model.

@@

actual_FL_pred
```
**Comment:**To test the accuracy of the complex model we decided to test our prediction on one case too. We chose Florida as our test state and as you can see from the summaries above our predictions are relatively close. The actual mean of interest in the term China Virus in Florida is 47.625 and our model predicted 46.10, this is only a 1.5 difference!
